Staged Abstract Interpreters

### 2018-11-15 paper/30_sai.tex
misc

\paragraph{Big-step vs Small-step.}
What we implemented is a big-step, compositional \todo{or semi-compositional} abstract interpreter, 
where the "compositional" means every recursive call of our abstract interpreter is applied with proper 
substructures of the current syntactic parameters. 
The compositionality ensures the specialization can be done by unfolding, as well as the termination of specialization procedure.
Nevertheless, it is also possible to specialize a small-step, operational abstract semantics --- \citeauthor{Johnson:2013:OAA:2500365.2500604}
showed this in abstract compilation \cite{Boucher:1996:ACN:647473.727587} style as one of their optimization 
to Abstract Abstract Machines \cite{Johnson:2013:OAA:2500365.2500604}. 
However, the generated abstract bytecodes still requires another small-step abstract machine 
to execute, which is an additional engineering efforts.
Another alternative approach for efficient specialization is to write the abstract interpreter 
in a big-step, monadic style \cite{DBLP:journals/pacmpl/DaraisLNH17}.

>>>>

\paragraph{Big-step vs Small-step.}
What we implemented is a big-step, compositional \todo{or semi-compositional} abstract interpreter, 
where the "compositional" means every recursive call of our abstract interpreter is applied with proper 
substructures of the current syntactic parameters \cite{10.1007/3-540-61580-6_11}.
The compositionality ensures the specialization can be done by unfolding, as well as the termination of specialization procedure.
Nevertheless, it is also possible to specialize a small-step, operational abstract semantics --- \citeauthor{Johnson:2013:OAA:2500365.2500604}
showed this in abstract compilation \cite{Boucher:1996:ACN:647473.727587} style as one of their optimizations
of Abstract Abstract Machines \cite{Johnson:2013:OAA:2500365.2500604}. 
However, the generated abstract bytecode still requires another small-step abstract machine 
to execute, which is an additional engineering efforts.
Another alternative approach for efficient specialization is to write the abstract interpreter 
in a big-step, monadic style \cite{DBLP:journals/pacmpl/DaraisLNH17}.
